Seismic signal enhancement based on the lowrank methods

### 2020-10-21 dtv/paper.tex
2020年10月20日 星期二 23时13分33秒 CDT

\begin{algorithm}
\caption{FWI with directional total variation}
\begin{algorithmic}[1]
  \scriptsize
  \STATE Initialize: $\mathbf{m}^0=\mathbf{m}_0$, and $\mathbf{a}_1^0=\mathbf{a}_2^0=\mathbf{b}_1^0=\mathbf{b}_2^0=0$\\
  \STATE While Iter $<$ MaxIter \\
  ~$\mathbf{m}^{k+1}=\min\limits_\mathbf{m} \mu || \mathbf{d} - f\left(\mathbf{m}\right) ||_2^2 + \lambda|| \mathbf{a}_1^k-\nabla_1 \mathbf{m}-\mathbf{b}_1^k||_2^2 + \lambda|| \mathbf{a}_2^k-\nabla_2 \mathbf{m}-\mathbf{b}_2^k||_2^2$  \\
  ~~~~~(Hint: we solve this subproblem using gradient method, and the gradient is: \\
  ~~~~~~~~$\mu f^{*} \left( f\left(\mathbf{m}^{k}\right) - \mathbf{d} \right) - \lambda \nabla^{T}_1 \left( \mathbf{a}_1^k-\nabla_1 \mathbf{m}^{k}-\mathbf{b}_1^k \right) - \lambda \nabla^{T}_2 \left( \mathbf{a}_2^k-\nabla_2 \mathbf{m}^{k}-\mathbf{b}_2^k \right)$) \\
  ~$\mathbf{a}_1^{k+1}=shrink\left(\nabla_1 \mathbf{m}^{k+1}+\mathbf{b}_1^k, \frac{1}{\lambda}\right)$ \\
  \new{~~~~~($shrink\left(x, \gamma\right) = \frac{x}{|x|} * max\left(|x| - \gamma, 0\right)$, a soft-thresholding operator \citep{donoho1995noising})} \\

  ~$\mathbf{a}_2^{k+1}=shrink\left(\nabla_2 \mathbf{m}^{k+1}+\mathbf{b}_2^k, \frac{1}{\lambda}\right)$ \\
  ~$\mathbf{b}_1^{k+1}=\mathbf{b}_1^{k} + \left(\nabla_1 \mathbf{m}^{k+1}-\mathbf{a}_1^{k+1}\right)$  \\
  ~$\mathbf{b}_2^{k+1}=\mathbf{b}_2^{k} + \left(\nabla_2 \mathbf{m}^{k+1}-\mathbf{a}_2^{k+1}\right)$  \\
  end
\end{algorithmic}
\end{algorithm}

>>>>

% Algorithm is not available in Madagascar online version (please refer to the journal version)
%\begin{algorithm}
%\caption{FWI with directional total variation}
%\begin{algorithmic}[1]
%  \scriptsize
%  \STATE Initialize: $\mathbf{m}^0=\mathbf{m}_0$, and $\mathbf{a}_1^0=\mathbf{a}_2^0=\mathbf{b}_1^0=\mathbf{b}_2^0=0$\\
%  \STATE While Iter $<$ MaxIter \\
%  ~$\mathbf{m}^{k+1}=\min\limits_\mathbf{m} \mu || \mathbf{d} - f\left(\mathbf{m}\right) ||_2^2 + \lambda|| \mathbf{a}_1^k-\nabla_1 \mathbf{m}-\mathbf{b}_1^k||_2^2 + \lambda|| \mathbf{a}_2^k-\nabla_2 \mathbf{m}-\mathbf{b}_2^k||_2^2$  \\
%  ~~~~~(Hint: we solve this subproblem using gradient method, and the gradient is: \\
%  ~~~~~~~~$\mu f^{*} \left( f\left(\mathbf{m}^{k}\right) - \mathbf{d} \right) - \lambda \nabla^{T}_1 \left( \mathbf{a}_1^k-\nabla_1 \mathbf{m}^{k}-\mathbf{b}_1^k \right) - \lambda \nabla^{T}_2 \left( \mathbf{a}_2^k-\nabla_2 \mathbf{m}^{k}-\mathbf{b}_2^k \right)$) \\
%  ~$\mathbf{a}_1^{k+1}=shrink\left(\nabla_1 \mathbf{m}^{k+1}+\mathbf{b}_1^k, \frac{1}{\lambda}\right)$ \\
%  \new{~~~~~($shrink\left(x, \gamma\right) = \frac{x}{|x|} * max\left(|x| - \gamma, 0\right)$, a soft-thresholding operator \citep{donoho1995noising})} \\
%  
%  ~$\mathbf{a}_2^{k+1}=shrink\left(\nabla_2 \mathbf{m}^{k+1}+\mathbf{b}_2^k, \frac{1}{\lambda}\right)$ \\
%  ~$\mathbf{b}_1^{k+1}=\mathbf{b}_1^{k} + \left(\nabla_1 \mathbf{m}^{k+1}-\mathbf{a}_1^{k+1}\right)$  \\
%  ~$\mathbf{b}_2^{k+1}=\mathbf{b}_2^{k} + \left(\nabla_2 \mathbf{m}^{k+1}-\mathbf{a}_2^{k+1}\right)$  \\
%  end
%\end{algorithmic}
%\end{algorithm}

### 2020-10-21 odrr3d/paper.tex
2020年10月20日 星期二 23时13分33秒 CDT

@@

\wen{\subsection{Rank-reduction method}
Regularization can be implemented as a rank-based constraint \wen{\cite[]{trickett2008,mssa,jinkun2015}}:
\begin{equation}
\label{eq:regu2}
\begin{split}
\hat{\mathbf{X}} &= \arg \min_{\mathbf{x}} \parallel\mathbf{D}-\mathbf{X} \parallel_F^2, \\ \text{subject to}&\quad \text{rank} (\mathcal{H}(\mathbf{X})) =N,
\end{split}
\end{equation}
%or in an unconstrained version as
%\begin{equation}
%\label{eq:regu2}
%\hat{\mathbf{X}} = \arg \min_{\mathbf{X}} \parallel\mathbf{D}-\mathbf{X} \parallel_F^2 + %\epsilon^2\text{rank} (\mathcal{H}(\mathbf{X})),
%\end{equation}
\wen{where} $\parallel\cdot\parallel_F$ denotes the Frobenius norm. $\mathbf{D}$ denotes a matrix constructed \dlo{by}\wen{from} the frequency slice corresponding to $w_0$. $\mathbf{X}$ denotes the noise-free data to be estimated. $\hat{\mathbf{X}}$ denotes the estimated signal. $\mathcal{H}(\mathbf{X})$ denotes the Hankel matrix constructed from $\mathbf{X}$. Let $\mathbf{M}=\mathcal{H}(\mathbf{D})$, the singular value decomposition of $\mathbf{M}$ can be expressed as 
\begin{equation}
\label{eq:svd}
\mathbf{M} = \mathbf{U}\boldsymbol{\Sigma}\mathbf{V}^H,
\end{equation}
where $\mathbf{U}$ and $\mathbf{V}$ are referred to as the left and right singular vector matrices, respectively. $\boldsymbol{\Sigma}$ is the singular value matrix. $(\cdot)^H$ denotes complex tranpose. According to equation \ref{eq:regu2}, the rank of the signal component that is embedded in the Hankel matrix $\mathbf{M}$ is assumed to be $N$. The traditional rank-reduction method based on the truncated singular value decomposition (TSVD) \cite[]{mssa} can be briefly expressed as
\begin{equation}
\label{eq:tsvd}
\hat{\mathbf{S}} = \mathbf{U}_N\boldsymbol{\Sigma}_N\mathbf{V}_N^H,
\end{equation}
which is a solution to equation \ref{eq:regu2} according to the Eckart-Young-Mirsky theorem \cite[]{eckart1936approximation}. $\hat{\mathbf{S}}$ denotes the denoised signal. $\mathbf{U}_N$ and $\mathbf{V}_N$ are matrices composed of the left $N$ singular vectors in $\mathbf{U}$ and $\mathbf{V}$, respectively. $\boldsymbol{\Sigma}_N$ is the truncated singular value matrix with the first $N$ singular values preserved.  Although theoretically $N$ equals to the number of distinct dipping components, it is practically defined as a relatively large number considering data complexity, otherwise signal energy can be damaged. The algorithm workflow for the traditional rank-reduction method (RR) is outlined in Algorithm \ref{alg:alg1}. $\mathcal{A}$ in the algorithm workflow denotes an averaging operator along anti-diagonals.}

\wen{\subsection{Damped rank-reduction method}
The estimated signal using the TSVD method, however, \dlo{is still containing}\wen{still contains} non-negligible residual noise components, as explained in \cite{weilin2016dmssa}. The problem of residual noise can be solved to some extent by further applying a thresholding operator to the singular value matrix according to the nuclear-norm minimization model \cite[]{yatong2017nuclear}:
\begin{equation}
\label{eq:nuclear}
\hat{\mathbf{S}} =\mathbf{U}_N\mathcal{T}(\boldsymbol{\Sigma}_N,\tau)\mathbf{V}_N^H,
\end{equation}
where $\mathcal{T}$ denotes the thresholding operator for the singular-values, and $\tau$ denotes the threshold of the operator. Defining an optimal threshold $\tau$, however, is often challenging because a constant threshold is inadequate to handle an inhomogeneous distribution of noise energy. \cite{weilin2016dmssa} developed a more elegant way to shrinkage the singular values by deriving a damping operator:
\begin{align}
\label{eq:damp}
\mathbf{P} &= \mathbf{I} - \boldsymbol{\Gamma}, \\
\label{eq:damp2}
\boldsymbol{\Gamma} &= \hat{\sigma}^K\left(\boldsymbol{\Sigma_N}\right)^{-K},
\end{align}
where $\mathbf{P}$ is called the damping matrix, $\mathbf{I}$ is an identity matrix, and $\boldsymbol{\Gamma}$ is referred to as the damping threshold matrix. $\hat{\sigma}$ is the $(N+1)$th singular value in the un-truncated singular matrix $\boldsymbol{\Sigma}$. \new{$K$ in equation \ref{eq:damp2} is called the damping factor}, which is used to control the strength of the damping operator. In a special case, when $K\rightarrow \infty$, $\mathbf{P}\rightarrow\mathbf{I}$, indicating that the damped rank-reduction method reverts to the traditional rank-reduction method. The mathematical details to derive the damping operator can be found in \cite{weilin2016dmssa} and \cite{weilin2017dlsp}. The damping operator is used to shrinkage the singular values in the TSVD formula to reduce the residual noise:
\begin{equation}
\label{eq:drr}
\hat{\mathbf{S}} = \mathbf{U}_N\mathbf{P}\boldsymbol{\Sigma}_N\mathbf{V}_N^H.
\end{equation}
Compared with the thresholding method in equation \ref{eq:nuclear}, where a rigid threshold $\tau$ is used to shrinkage the singular values, the damping operator applies variable thresholds to different singular values. According to equation \ref{eq:damp}, the threshold decreases as the residual noise becomes less dominant, i.e., the singular value becomes larger. The algorithm workflow for the damped rank-reduction method (DRR) is outlined in Algorithm \ref{alg:alg2}.}

@@

 The adaptive weighting operator can be applied to make the traditional rank-reduction method adaptive:
\begin{equation}
\label{eq:opts}
\hat{\mathbf{S}}=\mathbf{U}_N\hat{\mathbf{W}}\boldsymbol{\Sigma}_N\mathbf{V}_N^H.
\end{equation}
To incorporate the adaptive weighting operator into the damped rank-reduction framework, we can introduce intermediate variables as 
\begin{align}
\label{eq:svds_qu}
\mathbf{U}_N^{Q} = \mathbf{U}_N,\\
\label{eq:svds_qs}
\boldsymbol{\Sigma}_N^{Q} = \hat{\mathbf{W}}\boldsymbol{\Sigma}_N,\\
\label{eq:svds_qv}
\mathbf{V}_N^{Q} = \mathbf{V}_N,
\end{align}
then equation \ref{eq:opts} turns into 
\begin{equation}
\label{eq:opts2}
\hat{\mathbf{S}}=\mathbf{U}_N^{Q}\boldsymbol{\Sigma}_N^{Q}\mathbf{V}_N^{Q}.
\end{equation}
It can be derived that the damping formula (equation \ref{eq:damp}) also holds for equation \ref{eq:opts2} but with the damping threshold matrix expressed as
\begin{equation}
\label{eq:dampt}
\boldsymbol{\Gamma} = \hat{\sigma}^K\left(\boldsymbol{\Sigma_N^Q}\right)^{-K},
\end{equation}
where the subscript $N$ denotes a sufficiently large rank parameter, as required by the derivations detailed in \cite{yangkang2019gji5d}.  The resulted final form of the optimally damped rank-reduction method then can be expressed as 
\begin{equation}
\label{eq:odrr}
\hat{\mathbf{S}} = \mathbf{U}_N\mathbf{P}\hat{\mathbf{W}}\boldsymbol{\Sigma}_N\mathbf{V}_N^H.
\end{equation}
The algorithm workflow for the optimally damped rank-reduction method (ODRR) is outlined in Algorithm \ref{alg:alg3}. Due to the existence of a weighting matrix in the proposed method, it is more convenient to choose the input rank parameter $N$ empirically in practice. As mentioned previously, the rank parameter $N$ is in practice set to a relatively large value to forestall damaging the signal. But in the proposed algorithm, even if a large $N$ is used, the algorithm can adaptively shrink the singular-values. Thus, \dlo{the}\wen{its} performance is not sensitive to the input rank parameter, in contrast to other related approaches \cite[]{mssa}. Because of the insensitivity, one can use a sufficiently large $N$ in processing complicated datasets without leaving strong residual noise in the result. The convenience in tuning parameters makes the rank-reduction related methods more computationally feasible in large-scale data processing, e.g., the 5D reconstruction problem \cite[]{yangkang2019gji5d}, since one no longer needs to tune the parameters many times while one trial is already computationally demanding.  A glossary describing the main mathematical notations are presented in Table \ref{tbl:glo}. The three methods are all variations of how the singular-values are thresholded. Simply speaking, the DRR method improves the RR method by introducing a damping operation and the ODRR method improves DRR method by further introducing a weighting operation.}

@@

\wen{
  \begin{algorithm}
   \caption{Seismic denoising \dlo{seismic data via}\wen{based on} rank-reduction method. }
   \textbf{Require:} Input \dlo{seismic }data $\mathbf{D}(t,x,y)$ and predefined rank $N$.
    \begin{algorithmic}[1]
    \State \textbf{Fourier transform along the time axis}: $\text{FFT}\left(\mathbf{D}(t,x,y)\right)\rightarrow \mathbf{D}(\omega,x,y)$, \wen{for a frequency slice $\omega$}
        \For{$w$ = $1,\cdots,N_{\omega}$}
     \State \textbf{Construct block Hankel matrix}: $\mathcal{H}(\mathbf{D}(\omega))\rightarrow \mathbf{M}$
     \State \textbf{Singular value decomposition}: $\text{SVD}(\mathbf{M},N)\rightarrow [\mathbf{U},\boldsymbol{\Sigma},\mathbf{V}]$
     \State \textbf{Rank reduction}: $\mathbf{U}\boldsymbol{\Sigma}\mathbf{V}^T\rightarrow \hat{\mathbf{S}}$
     \State \textbf{Averaging}: $\mathcal{A}(\hat{\mathbf{S}})\rightarrow \hat{\mathbf{D}}(\omega)$
        \EndFor 
         \State \textbf{Inverse Fourier transform}: $\text{IFFT}\left(\hat{\mathbf{D}}(\omega,x,y)\right)\rightarrow \hat{\mathbf{D}}(t,x,y)$
\end{algorithmic}
\label{alg:alg1}
\end{algorithm}
  \begin{algorithm}
   \caption{Seismic denoising based on the damped rank-reduction method. }
   \textbf{Require:} \wen{Input seismic data $\mathbf{D}(t,x,y)$, predefined rank $N$, and damping factor $K$.}
    \begin{algorithmic}[1]
    \State \textbf{Fourier transform along the time axis}: $\text{FFT}\left(\mathbf{D}(t,x,y)\right)\rightarrow \mathbf{D}(\omega,x,y)$, \wen{for a frequency slice $\omega$}
        \For{$w$ = $1,\cdots,N_{\omega}$}
     \State \textbf{Construct block Hankel matrix}: $\mathcal{H}(\mathbf{D}(\omega))\rightarrow \mathbf{M}$
     \State \textbf{Singular value decomposition}: $\text{SVD}(\mathbf{M},N)\rightarrow [\mathbf{U},\boldsymbol{\Sigma},\mathbf{V}]$
     \State \textbf{Rank reduction with the damping operation}: $\mathbf{U}\mathbf{P}\boldsymbol{\Sigma}\mathbf{V}^T\rightarrow \hat{\mathbf{S}}$
     \State \textbf{Averaging}: $\mathcal{A}(\hat{\mathbf{S}})\rightarrow \hat{\mathbf{D}}(\omega)$
        \EndFor 
         \State \textbf{Inverse Fourier transform}: $\text{IFFT}\left(\hat{\mathbf{D}}(\omega,x,y)\right)\rightarrow \hat{\mathbf{D}}(t,x,y)$
\end{algorithmic}
\label{alg:alg2}
\end{algorithm}
  \begin{algorithm}
   \caption{Seismic denoising based on the optimally damped rank-reduction method. }
   \textbf{Require:} \wen{Input seismic data $\mathbf{D}(t,x,y)$, predefined rank $N$, and damping factor $K$.}
    \begin{algorithmic}[1]
    \State \textbf{Fourier transform along the time axis}: $\text{FFT}\left(\mathbf{D}(t,x,y)\right)\rightarrow \mathbf{D}(\omega,x,y)$, \wen{for a frequency slice $\omega$}
        \For{$w$ = $1,\cdots,N_{\omega}$}
     \State \textbf{Construct block Hankel matrix}: $\mathcal{H}(\mathbf{D}(\omega))\rightarrow \mathbf{M}$
     \State \textbf{Singular value decomposition}: $\text{SVD}(\mathbf{M},N)\rightarrow [\mathbf{U},\boldsymbol{\Sigma},\mathbf{V}]$
     \State \textbf{Rank reduction with both weighting and damping operations}: $\mathbf{U}\mathbf{P}\hat{\mathbf{W}}\boldsymbol{\Sigma}\mathbf{V}^T\rightarrow \hat{\mathbf{S}}$
     \State \textbf{Averaging}: $\mathcal{A}(\hat{\mathbf{S}})\rightarrow \hat{\mathbf{D}}(\omega)$
        \EndFor 
         \State \textbf{Inverse Fourier transform}: $\text{IFFT}\left(\hat{\mathbf{D}}(\omega,x,y)\right)\rightarrow \hat{\mathbf{D}}(t,x,y)$
\end{algorithmic}
\label{alg:alg3}
\end{algorithm}}

>>>>

\published{Geophysical Prospecting, 68, 2783-2807, (2020)}

@@

\wen{\subsection{Rank-reduction method}
Regularization can be implemented as a rank-based constraint \wen{\cite[]{trickett2008,mssa,jinkun2015}}:
\begin{equation}
\label{eq:regu2}
\begin{split}
\hat{\mathbf{X}} &= \arg \min_{\mathbf{x}} \parallel\mathbf{D}-\mathbf{X} \parallel_F^2, \\ \text{subject to}&\quad \text{rank} (\mathcal{H}(\mathbf{X})) =N,
\end{split}
\end{equation}
%or in an unconstrained version as
%\begin{equation}
%\label{eq:regu2}
%\hat{\mathbf{X}} = \arg \min_{\mathbf{X}} \parallel\mathbf{D}-\mathbf{X} \parallel_F^2 + %\epsilon^2\text{rank} (\mathcal{H}(\mathbf{X})),
%\end{equation}
\wen{where} $\parallel\cdot\parallel_F$ denotes the Frobenius norm. $\mathbf{D}$ denotes a matrix constructed \dlo{by}\wen{from} the frequency slice corresponding to $w_0$. $\mathbf{X}$ denotes the noise-free data to be estimated. $\hat{\mathbf{X}}$ denotes the estimated signal. $\mathcal{H}(\mathbf{X})$ denotes the Hankel matrix constructed from $\mathbf{X}$. Let $\mathbf{M}=\mathcal{H}(\mathbf{D})$, the singular value decomposition of $\mathbf{M}$ can be expressed as 
\begin{equation}
\label{eq:svd}
\mathbf{M} = \mathbf{U}\boldsymbol{\Sigma}\mathbf{V}^H,
\end{equation}
where $\mathbf{U}$ and $\mathbf{V}$ are referred to as the left and right singular vector matrices, respectively. $\boldsymbol{\Sigma}$ is the singular value matrix. $(\cdot)^H$ denotes complex tranpose. According to equation \ref{eq:regu2}, the rank of the signal component that is embedded in the Hankel matrix $\mathbf{M}$ is assumed to be $N$. The traditional rank-reduction method based on the truncated singular value decomposition (TSVD) \cite[]{mssa} can be briefly expressed as
\begin{equation}
\label{eq:tsvd}
\hat{\mathbf{S}} = \mathbf{U}_N\boldsymbol{\Sigma}_N\mathbf{V}_N^H,
\end{equation}
which is a solution to equation \ref{eq:regu2} according to the Eckart-Young-Mirsky theorem \cite[]{eckart1936approximation}. $\hat{\mathbf{S}}$ denotes the denoised signal. $\mathbf{U}_N$ and $\mathbf{V}_N$ are matrices composed of the left $N$ singular vectors in $\mathbf{U}$ and $\mathbf{V}$, respectively. $\boldsymbol{\Sigma}_N$ is the truncated singular value matrix with the first $N$ singular values preserved.  Although theoretically $N$ equals to the number of distinct dipping components, it is practically defined as a relatively large number considering data complexity, otherwise signal energy can be damaged. The algorithm workflow for the traditional rank-reduction method (RR) is outlined in Algorithm 1. $\mathcal{A}$ in the algorithm workflow denotes an averaging operator along anti-diagonals.}

\wen{\subsection{Damped rank-reduction method}
The estimated signal using the TSVD method, however, \dlo{is still containing}\wen{still contains} non-negligible residual noise components, as explained in \cite{weilin2016dmssa}. The problem of residual noise can be solved to some extent by further applying a thresholding operator to the singular value matrix according to the nuclear-norm minimization model \cite[]{yatong2017nuclear}:
\begin{equation}
\label{eq:nuclear}
\hat{\mathbf{S}} =\mathbf{U}_N\mathcal{T}(\boldsymbol{\Sigma}_N,\tau)\mathbf{V}_N^H,
\end{equation}
where $\mathcal{T}$ denotes the thresholding operator for the singular-values, and $\tau$ denotes the threshold of the operator. Defining an optimal threshold $\tau$, however, is often challenging because a constant threshold is inadequate to handle an inhomogeneous distribution of noise energy. \cite{weilin2016dmssa} developed a more elegant way to shrinkage the singular values by deriving a damping operator:
\begin{align}
\label{eq:damp}
\mathbf{P} &= \mathbf{I} - \boldsymbol{\Gamma}, \\
\label{eq:damp2}
\boldsymbol{\Gamma} &= \hat{\sigma}^K\left(\boldsymbol{\Sigma_N}\right)^{-K},
\end{align}
where $\mathbf{P}$ is called the damping matrix, $\mathbf{I}$ is an identity matrix, and $\boldsymbol{\Gamma}$ is referred to as the damping threshold matrix. $\hat{\sigma}$ is the $(N+1)$th singular value in the un-truncated singular matrix $\boldsymbol{\Sigma}$. \new{$K$ in equation \ref{eq:damp2} is called the damping factor}, which is used to control the strength of the damping operator. In a special case, when $K\rightarrow \infty$, $\mathbf{P}\rightarrow\mathbf{I}$, indicating that the damped rank-reduction method reverts to the traditional rank-reduction method. The mathematical details to derive the damping operator can be found in \cite{weilin2016dmssa} and \cite{weilin2017dlsp}. The damping operator is used to shrinkage the singular values in the TSVD formula to reduce the residual noise:
\begin{equation}
\label{eq:drr}
\hat{\mathbf{S}} = \mathbf{U}_N\mathbf{P}\boldsymbol{\Sigma}_N\mathbf{V}_N^H.
\end{equation}
Compared with the thresholding method in equation \ref{eq:nuclear}, where a rigid threshold $\tau$ is used to shrinkage the singular values, the damping operator applies variable thresholds to different singular values. According to equation \ref{eq:damp}, the threshold decreases as the residual noise becomes less dominant, i.e., the singular value becomes larger. The algorithm workflow for the damped rank-reduction method (DRR) is outlined in Algorithm 2.}

@@

 The adaptive weighting operator can be applied to make the traditional rank-reduction method adaptive:
\begin{equation}
\label{eq:opts}
\hat{\mathbf{S}}=\mathbf{U}_N\hat{\mathbf{W}}\boldsymbol{\Sigma}_N\mathbf{V}_N^H.
\end{equation}
To incorporate the adaptive weighting operator into the damped rank-reduction framework, we can introduce intermediate variables as 
\begin{align}
\label{eq:svds_qu}
\mathbf{U}_N^{Q} = \mathbf{U}_N,\\
\label{eq:svds_qs}
\boldsymbol{\Sigma}_N^{Q} = \hat{\mathbf{W}}\boldsymbol{\Sigma}_N,\\
\label{eq:svds_qv}
\mathbf{V}_N^{Q} = \mathbf{V}_N,
\end{align}
then equation \ref{eq:opts} turns into 
\begin{equation}
\label{eq:opts2}
\hat{\mathbf{S}}=\mathbf{U}_N^{Q}\boldsymbol{\Sigma}_N^{Q}\mathbf{V}_N^{Q}.
\end{equation}
It can be derived that the damping formula (equation \ref{eq:damp}) also holds for equation \ref{eq:opts2} but with the damping threshold matrix expressed as
\begin{equation}
\label{eq:dampt}
\boldsymbol{\Gamma} = \hat{\sigma}^K\left(\boldsymbol{\Sigma_N^Q}\right)^{-K},
\end{equation}
where the subscript $N$ denotes a sufficiently large rank parameter, as required by the derivations detailed in \cite{yangkang2019gji5d}.  The resulted final form of the optimally damped rank-reduction method then can be expressed as 
\begin{equation}
\label{eq:odrr}
\hat{\mathbf{S}} = \mathbf{U}_N\mathbf{P}\hat{\mathbf{W}}\boldsymbol{\Sigma}_N\mathbf{V}_N^H.
\end{equation}
The algorithm workflow for the optimally damped rank-reduction method (ODRR) is outlined in Algorithm 3. Due to the existence of a weighting matrix in the proposed method, it is more convenient to choose the input rank parameter $N$ empirically in practice. As mentioned previously, the rank parameter $N$ is in practice set to a relatively large value to forestall damaging the signal. But in the proposed algorithm, even if a large $N$ is used, the algorithm can adaptively shrink the singular-values. Thus, \dlo{the}\wen{its} performance is not sensitive to the input rank parameter, in contrast to other related approaches \cite[]{mssa}. Because of the insensitivity, one can use a sufficiently large $N$ in processing complicated datasets without leaving strong residual noise in the result. The convenience in tuning parameters makes the rank-reduction related methods more computationally feasible in large-scale data processing, e.g., the 5D reconstruction problem \cite[]{yangkang2019gji5d}, since one no longer needs to tune the parameters many times while one trial is already computationally demanding.  A glossary describing the main mathematical notations are presented in Table \ref{tbl:glo}. The three methods are all variations of how the singular-values are thresholded. Simply speaking, the DRR method improves the RR method by introducing a damping operation and the ODRR method improves DRR method by further introducing a weighting operation.}

@@

% Algorithm is not available in Madagascar online version (please refer to the journal version)
%\wen{
%  \begin{algorithm}
%   \caption{Seismic denoising \dlo{seismic data via}\wen{based on} rank-reduction method. }
%   \textbf{Require:} Input \dlo{seismic }data $\mathbf{D}(t,x,y)$ and predefined rank $N$.
%    \begin{algorithmic}[1]
%    \State \textbf{Fourier transform along the time axis}: $\text{FFT}\left(\mathbf{D}(t,x,y)\right)\rightarrow \mathbf{D}(\omega,x,y)$, \wen{for a frequency slice $\omega$}
%        \For{$w$ = $1,\cdots,N_{\omega}$}
%     \State \textbf{Construct block Hankel matrix}: $\mathcal{H}(\mathbf{D}(\omega))\rightarrow \mathbf{M}$
%     \State \textbf{Singular value decomposition}: $\text{SVD}(\mathbf{M},N)\rightarrow [\mathbf{U},\boldsymbol{\Sigma},\mathbf{V}]$
%     \State \textbf{Rank reduction}: $\mathbf{U}\boldsymbol{\Sigma}\mathbf{V}^T\rightarrow \hat{\mathbf{S}}$
%     \State \textbf{Averaging}: $\mathcal{A}(\hat{\mathbf{S}})\rightarrow \hat{\mathbf{D}}(\omega)$
%        \EndFor 
%         \State \textbf{Inverse Fourier transform}: $\text{IFFT}\left(\hat{\mathbf{D}}(\omega,x,y)\right)\rightarrow \hat{\mathbf{D}}(t,x,y)$
%\end{algorithmic}
%\label{alg:alg1}
%\end{algorithm}
%  \begin{algorithm}
%   \caption{Seismic denoising based on the damped rank-reduction method. }
%   \textbf{Require:} \wen{Input seismic data $\mathbf{D}(t,x,y)$, predefined rank $N$, and damping factor $K$.}
%    \begin{algorithmic}[1]
%    \State \textbf{Fourier transform along the time axis}: $\text{FFT}\left(\mathbf{D}(t,x,y)\right)\rightarrow \mathbf{D}(\omega,x,y)$, \wen{for a frequency slice $\omega$}
%        \For{$w$ = $1,\cdots,N_{\omega}$}
%     \State \textbf{Construct block Hankel matrix}: $\mathcal{H}(\mathbf{D}(\omega))\rightarrow \mathbf{M}$
%     \State \textbf{Singular value decomposition}: $\text{SVD}(\mathbf{M},N)\rightarrow [\mathbf{U},\boldsymbol{\Sigma},\mathbf{V}]$
%     \State \textbf{Rank reduction with the damping operation}: $\mathbf{U}\mathbf{P}\boldsymbol{\Sigma}\mathbf{V}^T\rightarrow \hat{\mathbf{S}}$
%     \State \textbf{Averaging}: $\mathcal{A}(\hat{\mathbf{S}})\rightarrow \hat{\mathbf{D}}(\omega)$
%        \EndFor 
%         \State \textbf{Inverse Fourier transform}: $\text{IFFT}\left(\hat{\mathbf{D}}(\omega,x,y)\right)\rightarrow \hat{\mathbf{D}}(t,x,y)$
%\end{algorithmic}
%\label{alg:alg2}
%\end{algorithm}
%  \begin{algorithm}
%   \caption{Seismic denoising based on the optimally damped rank-reduction method. }
%   \textbf{Require:} \wen{Input seismic data $\mathbf{D}(t,x,y)$, predefined rank $N$, and damping factor $K$.}
%    \begin{algorithmic}[1]
%    \State \textbf{Fourier transform along the time axis}: $\text{FFT}\left(\mathbf{D}(t,x,y)\right)\rightarrow \mathbf{D}(\omega,x,y)$, \wen{for a frequency slice $\omega$}
%        \For{$w$ = $1,\cdots,N_{\omega}$}
%     \State \textbf{Construct block Hankel matrix}: $\mathcal{H}(\mathbf{D}(\omega))\rightarrow \mathbf{M}$
%     \State \textbf{Singular value decomposition}: $\text{SVD}(\mathbf{M},N)\rightarrow [\mathbf{U},\boldsymbol{\Sigma},\mathbf{V}]$
%     \State \textbf{Rank reduction with both weighting and damping operations}: $\mathbf{U}\mathbf{P}\hat{\mathbf{W}}\boldsymbol{\Sigma}\mathbf{V}^T\rightarrow \hat{\mathbf{S}}$
%     \State \textbf{Averaging}: $\mathcal{A}(\hat{\mathbf{S}})\rightarrow \hat{\mathbf{D}}(\omega)$
%        \EndFor 
%         \State \textbf{Inverse Fourier transform}: $\text{IFFT}\left(\hat{\mathbf{D}}(\omega,x,y)\right)\rightarrow \hat{\mathbf{D}}(t,x,y)$
%\end{algorithmic}
%\label{alg:alg3}
%\end{algorithm}}
